Reconstructing Propositional Proofs in Type Theory

### 2017-11-21 paper/sections/introduction.tex
[ paper ] proof by derivation.

This paper has been organized in the following way.  In
Section~\ref{sec:type-theory}, some limitations of type theory are
discussed from proof-reconstruction point view.  In
Section~\ref{sec:metis-language-and-proofs}, we introduce the \Metis
prover.  In Section~\ref{sec:proof-reconstruction}, we show our
approach to reconstruct \Metis proofs.  Related work is described in
Section~\ref{sec:related-work}.  Conclusions and suggestions for
future work are presented in Section~\ref{sec:conclusions}.

@@

  \item The \verb!agda-metis! library as a formalization in \Agda to
  justify \Metis proofs of classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.

>>>>

This paper has been organized in the following way.  In
Section~\ref{sec:type-theory}, some limitations of type theory are
discussed from proof-reconstruction point view.  In
Section~\ref{sec:metis-language-and-proofs}, we introduce the \Metis
prover.  In Section~\ref{sec:proof-reconstruction}, we show our
approach to reconstruct \Metis derivations.  Related work is described in
Section~\ref{sec:related-work}.  Conclusions and suggestions for
future work are presented in Section~\ref{sec:conclusions}.

@@

  \item The \verb!agda-metis! library as a formalization in \Agda to
  justify \Metis derivations of classical propositional logic:
  \url{http://github.com/jonaprieto/agda-prop}.

### 2017-11-21 paper/sections/metis-language-and-proofs.tex
[ paper ] proof by derivation.

These proofs are directed acyclic graphs, trees of refutations
Each node stands for an application of an inference rule and the leaves
in the tree represent formulas in the given problem. Each node is
labeled with a name of the inference rule (\eg, \canonicalize).
Each edge links a premise with one conclusion.
The proof graphs have at their root the conclusion
$⊥$, since \Metis proofs are refutations.

\begin{figure}[!ht]
\centering
  \begin{bprooftree}\tt
    \AxiomC{}
    \RightLabel{negate}
    \UnaryInfC{$\neg p$}
    \RightLabel{strip}
    \UnaryInfC{$\neg p$}
    \AxiomC{}
    \RightLabel{axiom}
    \UnaryInfC{$p$}
    \RightLabel{canonicalize}
    \UnaryInfC{$p$}
    \RightLabel{simplify}
    \BinaryInfC{$⊥$}
    \RightLabel{canonicalize}
    \UnaryInfC{$⊥$}
  \end{bprooftree}
  \caption{\Metis proof tree of derivation in Example~\ref{fig:metis-example-tree}.}
  \label{fig:metis-example}
\end{figure}

>>>>

These proofs are directed acyclic graphs, trees of refutations
Each node stands for an application of an inference rule and the leaves
in the tree represent formulas in the given problem. Each node is
labeled with a name of the inference rule (\eg, \canonicalize).
Each edge links a premise with one conclusion.
The proof graphs have at their root the conclusion
$⊥$, since \Metis derivations are refutations.

\begin{figure}[!ht]
\centering
  \begin{bprooftree}\tt
    \AxiomC{}
    \RightLabel{negate}
    \UnaryInfC{$\neg p$}
    \RightLabel{strip}
    \UnaryInfC{$\neg p$}
    \AxiomC{}
    \RightLabel{axiom}
    \UnaryInfC{$p$}
    \RightLabel{canonicalize}
    \UnaryInfC{$p$}
    \RightLabel{simplify}
    \BinaryInfC{$⊥$}
    \RightLabel{canonicalize}
    \UnaryInfC{$⊥$}
  \end{bprooftree}
  \caption{\Metis derivation tree of derivation in Example~\ref{fig:metis-example-tree}.}
  \label{fig:metis-example}
\end{figure}
